---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 12pt
    geometry:
      - margin=1in
      - heightrounded
    include-in-header:
      - preamble_cv.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---
\begingroup
\par\centering{\LARGE{Theodore Warren Hermann, Ph.D.}}
\vspace{-5pt}
\par\centering {\large\Letter} ted.w.hermann@gmail.com
\vspace{-5pt}
\par\centering Homepage: \href{https://mrguyperson.quarto.pub}{mrguyperson.quarto.pub}
\vspace{-5pt}
\par\centering LinkedIn: \href{https://www.linkedin.com/in/theodorewhermann/}{linkedin.com/in/theodorewhermann}
\vspace{-5pt}
\par\centering GitHub: \href{https://www.github.com/mrguyperson}{github.com/mrguyperson}
\vspace{-5pt}
\par\centering Researchgate: \href{https://www.researchgate.net/profile/Theodore-Hermann}{researchgate.net/profile/Theodore-Hermann}

\endgroup

```{r}
#| name: setup
library(tidyverse)
library(readxl)
library(here)
library(glue)

source(here("functions", "functions.R"))

path <- here("cv", "publications.xlsx")


```

# Professional Summary

I am a scientist and software practitioner with training in ecology and quantitative methods, and several years of hands-on experience building data workflows, predictive models, and reproducible research systems. I enjoy moving between domains, whether ecology, resource management, or environmental systems, and applying rigorous, transparent computational tools to real problems. My work emphasizes clarity, modularity, and reproducibility, and I am comfortable in languages and environments such as R, Python, Julia, bash, Docker, Git, and Linux. I thrive in multidisciplinary settings, collaborating across teams and translating technical results into accessible forms for decision makers, stakeholders, or broader audiences.

# Education

2018\. Ph.D., Biology. The State University of New York–College of Environmental Science and Forestry (SUNY–ESF). Syracuse, NY, USA.

* Dissertation: *Migrations of neotropical freshwater fishes inferred from otolith microchemistry and larval drift: conservation implications* 
* Adviser: Donald J. Stewart, Ph.D.

2013\. M.P.A., Public Administration. Syracuse University. Syracuse, NY, USA.

2009\. B.S., Science of Earth Systems. Cornell University. Ithaca, NY, USA.

# Professional experience

```{r}
#| name: jobs
#| results: asis

read_excel(path, sheet = "experience") %>%
    rowid_to_column() %>%
    mutate(
        across(start:end, dmy),
        month_start = month(start, label = TRUE, abbr = TRUE),
        end = if_else(is.na(end), today(), end),
        month_end = month(end, label = TRUE, abbr = TRUE),
        date_range = glue(
            "{month_start} {year(start)}--{month_end} {year(end)}"
        ),
        jobs = glue(
            "{rowid}. {date_range}. **{title}**, {organization}."
        )
    ) %>% 
    pull(jobs)

```


# Peer-reviewed publications
```{r}
#| name: publications
#| results: asis

read_excel(path, sheet = "publications") %>%
    mutate(
        pub_date = replace_na(pub_date, today()),
        journal = case_when(
            is.na(journal) & category == "in_prep" ~ "In prep",
            is.na(journal) & category == "in_review" ~ "In review",
            .default = journal
        )
        ) %>%
    arrange(desc(pub_date), category) %>%
    rowid_to_column() %>%
    mutate(
        citation = if_else(
            category == "peer_reviewed",
            glue("{rowid}. {author} {year}. {title}. *{journal}*. {number}. DOI: [{doi}](https://doi.org/{doi})"),
            glue("{rowid}. {author} {title}. *{journal}*.")
    )) %>% select(citation) %>%
    pull(citation)


```

# Teaching experience

```{r}
#| name: teaching
#| results: asis

read_excel(path, sheet = "teaching") %>%
    arrange(-year, semester) %>%
    rowid_to_column() %>%
    mutate(
        teaching = glue(
            "{rowid}. {stringr::str_to_title(semester)}, {year}. **{course}**, {institution}. {title}."
        )
    ) %>% pull(teaching)

```

# Presentations

## Conference posters

```{r}
#| name: posters
#| results: asis
read_excel(path, sheet = "presentations") %>%
    filter(grepl("Poster", type)) %>%
    arrange(-year) %>%
    rowid_to_column() %>%
    mutate(
        posters = glue(
            "{rowid}. {names} {title}. {event}, {location}. {date}."
        )
    ) %>%
    pull(posters)

```

## Guest lectures

```{r}
#| name: posters
#| results: asis
read_excel(path, sheet = "presentations") %>%
    filter(grepl("Guest", type)) %>%
    arrange(-year) %>%
    rowid_to_column() %>%
    mutate(
        guest_lectures = glue(
            "{rowid}. {names} {title}. {event}, {location}. {date}."
        )
    ) %>%
    pull(guest_lectures)

```

# Grants, honors, and awards

```{r}
#| name: awards
#| results: asis
read_excel(path, sheet = "awards") %>%
    arrange(-year) %>%
    rowid_to_column() %>%
    mutate(
        awards = glue(
            "{rowid}. **{award}**. {status}, {year}."
        )
    ) %>% pull(awards)

```

# Reviewer
*Ad hoc* reviewer for:

```{r}
#| results: asis
read_excel(path, sheet = "reviewer") %>%
    arrange(journal) %>%
    distinct(journal) %>%
    mutate(journal = glue(
        "* {journal}"
    )) %>%
    pull(journal)

```

``` {r}
#| name: skills

skill_data <- read_excel(path, sheet = "skills") %>%
    group_by(order) %>%
    arrange(order, .by_group = TRUE) %>%
    ungroup() %>%
    mutate(skill = glue("* {skill}"))

categories <- c("technique", "programming_language", "tool", "language", "soft_skill")
formatted_skills <- map(categories, ~ filter_and_pull(skill_data, type, .x, skill))

techniques <- formatted_skills[[1]]
code <- formatted_skills[[2]]
tools <- formatted_skills[[3]]
languages <- formatted_skills[[4]]
soft_skills <- formatted_skills[[5]]

```

# Programming Languages

``` {r} 
#| results: asis
code

```

# Tech Tools

``` {r} 
#| results: asis
tools

```

# Quantitative Skills

``` {r} 
#| results: asis
techniques

```

# Language Skills

``` {r} 
#| results: asis
languages

```

# Soft Skills

``` {r} 
#| results: asis
soft_skills

```