---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 12pt
    geometry:
      - margin=1in
      - heightrounded
    include-in-header:
      - preamble_cv.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---
\begingroup
\par\centering{\LARGE{Theodore Warren Hermann, Ph.D.}}
\vspace{-5pt}
\par\centering {\large\Letter} ted.w.hermann@gmail.com
\vspace{-5pt}
\par\centering Homepage: \href{https://mrguyperson.quarto.pub}{mrguyperson.quarto.pub}
\vspace{-5pt}
\par\centering LinkedIn: \href{https://www.linkedin.com/in/theodorewhermann/}{linkedin.com/in/theodorewhermann}
\vspace{-5pt}
\par\centering GitHub: \href{https://www.github.com/mrguyperson}{github.com/mrguyperson}
\vspace{-5pt}
\par\centering Researchgate: \href{https://www.researchgate.net/profile/Theodore-Hermann}{researchgate.net/profile/Theodore-Hermann}

\endgroup

```{r}
#| name: setup
library(tidyverse)
library(readxl)
library(here)
library(glue)

path <- here("cv", "publications.xlsx")


```

# Professional Summary

I hold a Ph.D. in Biology and an M.P.A. in Public Administration, with a research background that spans freshwater ecology, species movement modeling, and agent-based simulation. At UC Santa Cruz, my postdoctoral work focused on simulating fish migration in modified river systems---collaborating across disciplines and time zones to build tools that supported evidence-based decision-making for water-resource managers. Earlier, my doctoral research applied biogeochemical markers---measured using laser ablation inductively coupled plasma mass spectrometry and scanning X-ray fluorescence microscopy---to reconstruct life-history patterns in migratory fish, linking fieldwork, laboratory chemistry, and ecological inference.

Beyond academia, I’ve worked extensively as a technical and copy editor for scientific manuscripts across fields like ecology, remote sensing, geology, machine learning, and medical trials. I’ve edited hundreds of papers—many for non-native English speakers---where I focused on improving clarity and impact without losing the author’s voice. I’ve also reviewed manuscripts for journals like *Aquatic Conservation* and *Ecology and Evolution*, giving me insight into the publishing process from both sides. This editorial experience complements my scientific training and strengthens my ability to communicate complex ideas clearly and diplomatically---an asset in working with stakeholders, translating methodologies, or contributing to policy-aligned frameworks.

My professional experience reflects a pattern: I’m comfortable jumping into new, open-ended challenges, learning rapidly, and devising practical solutions. I’m drawn to roles that require cross-functional thinking, methodological rigor, and strategic communication---especially when they serve a broader mission of ecological sustainability and systems change. 


# Education

2018\. Ph.D., Biology. The State University of New York–College of Environmental Science and Forestry (SUNY–ESF). Syracuse, NY, USA.

* Dissertation: *Migrations of neotropical freshwater fishes inferred from otolith microchemistry and larval drift: conservation implications* 
* Adviser: Donald J. Stewart, Ph.D.

2013\. M.P.A., Public Administration. Syracuse University. Syracuse, NY, USA.

2009\. B.S., Science of Earth Systems. Cornell University. Ithaca, NY, USA.

# Professional experience

```{r}
#| name: jobs
#| results: asis

read_excel(path, sheet = "experience") %>%
    rowid_to_column() %>%
    mutate(
        month_start = month(start, label = TRUE, abbr = TRUE),
        month_end = month(end, label = TRUE, abbr = TRUE),
        date_range = glue(
            "{month_start} {year(start)}--{month_end} {year(end)}"
        ),
        jobs = glue(
            "{rowid}. {date_range}. **{title}**, {organization}."
        )
    ) %>% pull(jobs)

```


# Peer-reviewed publications
```{r}
#| name: publications
#| results: asis

read_excel(path, sheet = "publications") %>%
    mutate(
        pub_date = replace_na(pub_date, today()),
        journal = case_when(
            is.na(journal) & category == "in_prep" ~ "In prep",
            is.na(journal) & category == "in_review" ~ "In review",
            .default = journal
        )
        ) %>%
    arrange(desc(pub_date), category) %>%
    rowid_to_column() %>%
    mutate(
        citation = if_else(
            category == "peer_reviewed",
            glue("{rowid}. {author} {year}. {title}. *{journal}*. {number}. DOI: [{doi}](https://doi.org/{doi})"),
            glue("{rowid}. {author} {title}. *{journal}*.")
    )) %>% select(citation) %>%
    pull(citation)


```

# Teaching experience

```{r}
#| name: teaching
#| results: asis

read_excel(path, sheet = "teaching") %>%
    arrange(-year, semester) %>%
    rowid_to_column() %>%
    mutate(
        teaching = glue(
            "{rowid}. {stringr::str_to_title(semester)}, {year}. **{course}**, {institution}. {title}."
        )
    ) %>% pull(teaching)

```

# Presentations

## Conference posters

```{r}
#| name: posters
#| results: asis
read_excel(path, sheet = "presentations") %>%
    filter(grepl("Poster", type)) %>%
    arrange(-year) %>%
    rowid_to_column() %>%
    mutate(
        posters = glue(
            "{rowid}. {names} {title}. {event}, {location}. {date}."
        )
    ) %>%
    pull(posters)

```

## Guest lectures

```{r}
#| name: posters
#| results: asis
read_excel(path, sheet = "presentations") %>%
    filter(grepl("Guest", type)) %>%
    arrange(-year) %>%
    rowid_to_column() %>%
    mutate(
        guest_lectures = glue(
            "{rowid}. {names} {title}. {event}, {location}. {date}."
        )
    ) %>%
    pull(guest_lectures)

```

# Grants, honors, and awards

```{r}
#| name: awards
#| results: asis
read_excel(path, sheet = "awards") %>%
    arrange(-year) %>%
    rowid_to_column() %>%
    mutate(
        awards = glue(
            "{rowid}. **{award}**. {status}, {year}."
        )
    ) %>% pull(awards)

```

# Reviewer
*Ad hoc* reviewer for:

```{r}
#| results: asis
read_excel(path, sheet = "reviewer") %>%
    arrange(journal) %>%
    distinct(journal) %>%
    mutate(journal = glue(
        "* {journal}"
    )) %>%
    pull(journal)

```
