---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 10pt
    geometry:
      - margin=.78in
      - heightrounded
    include-in-header:
      - preamble_resume.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---
<!-- 
\newpage
\thispagestyle{empty} -->
<!-- \begingroup
\par\centering{\LARGE{Theodore Warren Hermann, Ph.D.}}
\vspace{-5pt}
\par\centering Lützenstraße 2, 10711 Berlin
\vspace{-10pt}
\par\centering {\large\Letter} ted.w.hermann@gmail.com
\vspace{-10pt}
\par\centering{{\large\Telefon} +49 176 544 06201}
\vspace{-10pt}
\par\centering Homepage: \href{https://mrguyperson.quarto.pub}{mrguyperson.quarto.pub}
\vspace{-10pt} -->
<!-- \par\centering GitHub: \href{https://www.github.com/mrguyperson}{github.com/mrguyperson}
\vspace{-10pt}
\par\centering LinkedIn: \href{https://www.linkedin.com/in/theodorewhermann/}{linkedin.com/in/theodorewhermann} -->
<!-- \par
\endgroup -->


```{r}
#| name: setup
library(tidyverse)
library(readxl)
library(here)
library(glue)

source(here("functions", "functions.R"))

path <- here("cv", "publications.xlsx")


```


```{r}
#| name: contact

contact_info <- read_excel(path, sheet = "contact")

email <- filter_and_pull(contact_info, value, "email")
city <- filter_and_pull(contact_info, value, "city")
website <- filter_and_pull(contact_info, value, "website")
phone <- filter_and_pull(contact_info, value, "phone")
```

\begingroup
\par\centering\textbf{Theodore W. Hermann, Ph.D.}
\vspace{-10pt}
\par\centering `r city` | [`r email`](mailto:`r email`) | `r phone`
\vspace{-10pt}
\par\centering Portfolio: [`r website`](`r website`)
\vspace{-10pt}

\endgroup


## Professional Summary

Detail-oriented biologist and data analyst with 7+ years of experience using machine learning, simulation, and statistical analysis to solve complex problems. Proven track record in building predictive models, automating workflows, and delivering insights to non-technical stakeholders. Skilled in Python, R, SQL, and Docker, with a passion for reproducibility and open-source solutions. Looking to apply strong quantitative skills and a scientific mindset to solve challenges in data-driven organizations.


``` {r}
#| name: skills

skill_data <- read_excel(path, sheet = "skills") %>%
    group_by(order) %>%
    arrange(order, .by_group = TRUE) %>%
    ungroup()

techniques <- filter_and_pull(skill_data, skill, "technique") %>%
    paste(collapse = ", ") %>%
    stringr::str_to_sentence()
code <- filter_and_pull(skill_data, skill, "programming_language") %>%
    paste(collapse = ", ")
tools <- filter_and_pull(skill_data, skill, "tool") %>%
    paste(collapse = ", ")
languages <- filter_and_pull(skill_data, skill, "language") %>%
    paste(collapse = ", ")
soft_skills <- filter_and_pull(skill_data, skill, "soft_skill") %>%
    paste(collapse = ", ") %>%
    stringr::str_to_sentence()

```
## Core Skills & Tools

* Code: `r code`
* Tools: `r tools`
* Techniques: `r techniques`
* Soft Skills: `r soft_skills`
* Languages: `r languages`


## Professional Experience
\par\vspace{-5pt}
```{r}
#| name: jobs

data <- read_excel(path, sheet = "experience") %>%
    mutate(in_short_form = as.logical(in_short_form)) %>%
    filter(in_short_form) %>%
    mutate(
        month_start = month(start, label = TRUE, abbr = TRUE),
        month_end = month(end, label = TRUE, abbr = TRUE),
        date_range = glue(
            "{month_start} {year(start)}--{month_end} {year(end)}"
        ),
        job_line = glue(
            "{date_range}: **{names_for_short}**, {organization}"
        ),
        task_list = map(tasks_for_short, ~str_split(.x, "\\*")[[1]])
    ) %>% 
    unnest(task_list) %>%
    mutate(
        bullet_tasks = glue(
            "* {task_list}"
        )
    )

jobs <- pull(data, job_line) %>% unique()

```

`r jobs[1]`

```{r}
#| results: asis

data %>%
    filter(job_line == jobs[1]) %>%
    pull(bullet_tasks)
```


`r jobs[2]`

```{r}
#| results: asis

data %>%
    filter(job_line == jobs[2]) %>%
    pull(bullet_tasks)
```


`r jobs[3]`

```{r}
#| results: asis

data %>%
    filter(job_line == jobs[3]) %>%
    pull(bullet_tasks)
```



## Education

2018\. **Ph.D.**, **Biology**. The State University of New York–College of Environmental Science and Forestry (SUNY–ESF). Syracuse, NY, USA.

2013\. **M.P.A.**, **Public Administration**. Syracuse University. Syracuse, NY, USA.

2009\. **B.S.**, **Science of Earth Systems**. Cornell University. Ithaca, NY, USA.