---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 10.5pt
    geometry:
      - margin=.78in
      - heightrounded
    include-in-header:
      - preamble_resume.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---
<!-- 
\newpage
\thispagestyle{empty} -->
\begingroup
\par\centering{\LARGE{Theodore Warren Hermann, Ph.D.}}
\vspace{-5pt}
\par\centering Lützenstraße 2, 10711 Berlin
\vspace{-10pt}
\par\centering {\large\Letter} ted.w.hermann@gmail.com
\vspace{-10pt}
\par\centering{{\large\Telefon} +49 176 544 06201}
\vspace{-10pt}
\par\centering Homepage: \href{https://mrguyperson.quarto.pub}{mrguyperson.quarto.pub}
\vspace{-10pt}
<!-- \par\centering GitHub: \href{https://www.github.com/mrguyperson}{github.com/mrguyperson}
\vspace{-10pt}
\par\centering LinkedIn: \href{https://www.linkedin.com/in/theodorewhermann/}{linkedin.com/in/theodorewhermann} -->
\par
\endgroup
```{r}
#| name: setup
library(tidyverse)
library(readxl)
library(here)
library(glue)

source(here("functions", "functions.R"))

path <- here("cv", "publications.xlsx")


```

``` {r}
#| name: skills

skill_data <- read_excel(path, sheet = "skills") 

skills <- filter_and_pull(skill_data, skill, "skill") %>%
    paste(collapse = ", ")
code <- filter_and_pull(skill_data, skill, "programming_language") %>%
    paste(collapse = ", ")
tech <- filter_and_pull(skill_data, skill, "tech") %>%
    paste(collapse = ", ")
languages <- filter_and_pull(skill_data, skill, "language") %>%
    paste(collapse = ", ")

```
# Summary
Skills: `r skills`
\par\vspace{-5pt}
Code: `r code`
\par\vspace{-5pt}
Tech: `r tech`
\par\vspace{-5pt}
Languages: `r languages`
\par\vspace{-5pt}
# Experience
\par\vspace{-5pt}
```{r}
#| name: jobs

data <- read_excel(path, sheet = "experience") %>%
    mutate(in_short_form = as.logical(in_short_form)) %>%
    filter(in_short_form) %>%
    mutate(
        month_start = month(start, label = TRUE, abbr = TRUE),
        month_end = month(end, label = TRUE, abbr = TRUE),
        date_range = glue(
            "{month_start} {year(start)}--{month_end} {year(end)}"
        ),
        job_line = glue(
            "{date_range}: **{names_for_short}**, {organization}"
        ),
        task_list = map(tasks_for_short, ~str_split(.x, "\\*")[[1]])
    ) %>% 
    unnest(task_list) %>%
    mutate(
        bullet_tasks = glue(
            "* {task_list}"
        )
    )

jobs <- pull(data, job_line) %>% unique()

```

`r jobs[1]`

```{r}
#| results: asis

data %>%
    filter(job_line == jobs[1]) %>%
    pull(bullet_tasks)
```


`r jobs[2]`

```{r}
#| results: asis

data %>%
    filter(job_line == jobs[2]) %>%
    pull(bullet_tasks)
```


`r jobs[3]`

```{r}
#| results: asis

data %>%
    filter(job_line == jobs[3]) %>%
    pull(bullet_tasks)
```



# Education

2018\. **Ph.D.**, **Biology**. The State University of New York–College of Environmental Science and Forestry (SUNY–ESF). Syracuse, NY, USA.

2013\. **M.P.A.**, **Public Administration**. Syracuse University. Syracuse, NY, USA.

2009\. **B.S.**, **Science of Earth Systems**. Cornell University. Ithaca, NY, USA.